---
title: "IS607 Project2"
author: "Param Singh"
date: "March 15, 2015"
output: html_document
---

I approached the analysis for this project by examining the data, looking at all four groupings at a high-level as a whole, and then conducting individual analysis. I used the results of the analysis drive my conclusions.

```{r}
require(ggplot2)
require(grid)
require(gridExtra)
# Data setup - I chose to treat these as separate data frames since the relationship between X and Y among the four groups was different
df1 <- data.frame( x = c(10.00, 8.00, 13.00, 9.00, 11.00, 14.00, 6.00, 4.00, 12.00, 7.00, 5.00), 
                   y = c(8.04, 6.95, 7.58, 8.81, 8.33, 9.96, 7.24, 4.26, 10.84, 4.82, 5.68) )

df2 <- data.frame( x = c(10.00, 8.00, 13.00, 9.00, 11.00, 14.00, 6.00, 4.00, 12.00, 7.00, 5.00), 
                   y = c(9.14, 8.14, 8.74, 8.77, 9.26, 8.10, 6.13, 3.10, 9.13, 7.26, 4.74) )

df3 <- data.frame( x = c(10.00, 8.00, 13.00, 9.00, 11.00, 14.00, 6.00, 4.00, 12.00, 7.00, 5.00), 
                   y = c(7.46, 6.77, 12.74, 7.11, 7.81, 8.84, 6.08, 5.39, 8.15, 6.42, 5.73) )

df4 <- data.frame( x = c(8.00, 8.00, 8.00, 8.00, 8.00, 8.00, 8.00, 19.00, 8.00, 8.00, 8.00), 
                   y = c(6.58, 5.76, 7.71, 8.84, 8.47, 7.04, 5.25, 12.50, 5.56, 7.91, 6.89) )
```

Overall plot of the different groups of data:

```{r, echo=FALSE}
p1 <- ggplot(df1, aes(x=x, y=y)) + geom_point(color='blue', size=3) + labs(title = '1')
p2 <- ggplot(df2, aes(x=x, y=y)) + geom_point(color ='green4', size=3, pch=17) + labs(title = '2')
p3 <- ggplot(df3, aes(x=x, y=y)) + geom_point(color='red', size=3, pch=23) + labs(title = '3')
p4 <- ggplot(df4, aes(x=x, y=y)) + geom_point() + labs(title = '4')
grid.arrange(p1, p2, p3, p4, ncol=2)
```

Analysis of the first group:
```{r}
summary(df1)
lm(data=df1)
p1 + geom_smooth(method="lm")
```

Analysis of the second group:
```{r}
summary(df2)
lm(data=df2)
p2 + geom_smooth(method="lm")
```

Analysis of the third group:
```{r}
summary(df3)
lm(data=df3)
p3 + geom_smooth(method="lm")
```

Analysis of the fourth group:
```{r}
summary(df4)
table(df4)
p4 + geom_boxplot()
```